Northern Pikeminnow Predation on Juvenile Chinook Salmon in Deadwater Slough, Salmon River, Idaho and Potential Impacts to Local Populations

### 2021-12-23 analysis/paper/paper.Rmd
cleaned up figures

```{r cpue-fig, fig.cap = "The number of Northern Pikeminnow caught per angler effort for each sampling event."}
total_cpue %>%
  ggplot(aes(x = event_name,
             y = catch_per_hr)) +
  geom_col(fill = "gray30") +
  labs(y = "Catch Per Angler Hour") +
  theme(axis.title.x = element_blank())

@@

```{r abund-fig, fig.cap = "Estimates of abundance of Northern Pikeminnow using different mark-recapture estimators and for the fall sampling events. Note the y-axis is truncated at 100."}
all_est %>%
  mutate(across(c(N, Lci, Uci),
                ~ . / 1000)) %>%
  ggplot(aes(x = model,
             y = N,
             color = model)) +
  geom_point(size = 4) +
  geom_errorbar(aes(ymin = Lci,
                    ymax = Uci),
                width = 0.1) +
  facet_wrap(~ event_name) +
  coord_cartesian(ylim = c(0, 100)) +
  labs(x = "Estimator",
       y = "Abundance (x 1,000)") +
  #theme_bw() +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 45,
                                   hjust = 1)) +
  scale_color_brewer(palette = "Dark2")

@@

```{r length-freq-p, eval = T, fig.cap = "A length frequency plot."}
length_freq_p = gastric_df %>%
  ggplot(aes(length)) +
  geom_histogram(breaks = seq(150, 650, by = 50),
                 col = "#DB740E",
                 fill = "#DB740E",
                 alpha = .2) +
  labs(x = "TL (mm)",
       y = "Frequency") +
  xlim(c(100, 700)) +
  ylim(c(0, 800)) +
  scale_x_continuous(breaks = seq(0, 650, by = 50)) +
  scale_y_continuous(breaks = seq(0, 550, by = 50)) +
  theme_classic()

@@

```{r bio-p, fig.cap = "Temp."}
spring_results$season = "Spring"
fall_results$season = "Fall"
bio_results = rbind(spring_results, fall_results)
bio_results$ymd = (ymd(bio_results$date))

pFish = bio_results %>%
  ggplot(aes(ymd, f50_g)) +
  geom_line(size = 1.15) +
  geom_ribbon(data = bio_results,
              aes(ymd,
                  ymin = f10_g,
                  ymax = f90_g),
              color = "grey65",
              alpha = 0.4) +
  theme_bw() +
  labs(y = "Cumulative fish consumed (g)",
       x = "",
       title = "") +
  facet_rep_wrap(~season,
                 scales = "free_x",
                 repeat.tick.labels = F) +
  theme(strip.background = element_rect(color = "white",
                                        fill = "white"),
        strip.text.x = element_text(size = 12),
        axis.text.x = element_blank(),
        axis.text.y = element_text(size = 11,
                                   color = "black"),
        axis.title.y = element_text(vjust = 1,
                                    size = 12),
        panel.grid.major.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.margin = unit(c(-.1, .3, -.3, .2), "cm"))

pTemp = bio_results %>%
  ggplot(aes(ymd, temperature_c)) +
  geom_line(color = "navyblue",
            size = 1.15) +
  theme_bw() +
  labs(y = expression("Water temperature"*~degree*C),
       x = "Month",
       title = "") +
  facet_rep_wrap(~season,
                 scales = "free_x",
                 repeat.tick.labels = F) +
  theme(strip.background = element_rect(color = "white",
                                        fill = "white"),
        strip.text.x = element_blank(),
        axis.text.x = element_text(size = 11,
                                   color = "black"),
        axis.title.x = element_text(size = 12),
        axis.text.y = element_text(size = 11,
                                   color = "black"),
        axis.title.y = element_text(vjust = 0.1,
                                    size = 12),
        panel.grid.major.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.margin = unit(c(-.1, .3, .1, .1), "cm"))

@@

```{r adult-imp-p, fig.cap = "How many Chinook Salmon are consumed by Northern Pikeminnow, depending on what percent of diet is Chinook. Faceted by migration season and life-stage."}
adult_impact %>%
  mutate(stage = "Juv. Emigrant") %>%
  select(stage,
         season,
         perc_diet,
         starts_with("smolt")) %>%
  rename_with(.fn = ~ str_remove(., "smolt_"),
              .cols = starts_with("smolt")) %>%
  bind_rows(adult_impact %>%
              mutate(stage = "Adult Equivalent") %>%
              select(stage,
                     season,
                     perc_diet,
                     starts_with("adult")) %>%
              rename_with(.fn = ~ str_remove(., "adult_"),
                          .cols = starts_with("adult"))) %>%
  ggplot(aes(x = perc_diet,
             y = N,
             color = as.factor(perc_diet))) +
  geom_errorbar(aes(ymin = Lci,
                    ymax = Uci),
                width = 0.1) +
  geom_point(size = 4) +
  facet_grid(fct_rev(stage) ~ season,
             scales = "free_y") +
  scale_color_viridis_d(name = "Percent Chinook\nin Diet") +
  theme(axis.text.x = element_blank(),
        legend.position = "bottom",
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank()) +
  labs(y = "Number Chinook Consumed")

>>>>

```{r cpue-fig, fig.cap = "The number of Northern Pikeminnow caught per angler effort for each sample effort."}
total_cpue %>%
  ggplot(aes(x = event_name,
             y = catch_per_hr)) +
  geom_col(fill = "gray30") +
  labs(y = "Catch Per Angler Hour") +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_text(size = 11,
                                   color = "black"),
        axis.title.y = element_text(vjust = 3),
        axis.text.y = element_text(size = 11,
                                   color = "black"))

@@

```{r abund-fig, fig.cap = "Estimates of abundance of Northern Pikeminnow using different mark-recapture estimators and for the fall sampling events. Note the y-axis is truncated at 100."}
all_est %>%
  mutate(across(c(N, Lci, Uci),
                ~ . / 1000)) %>%
  ggplot(aes(x = model,
             y = N,
             color = model)) +
  geom_point(size = 4) +
  geom_errorbar(aes(ymin = Lci,
                    ymax = Uci),
                width = 0.1) +
  facet_wrap(~ event_name) +
  coord_cartesian(ylim = c(0, 100)) +
  labs(x = "Estimator",
       y = "Abundance (x 1,000)") +
  #theme_bw() +
  theme(legend.position = "none",
        axis.title.x = element_blank(),
        axis.text.x = element_text(angle = 45,
                                   hjust = 1,
                                   size = 11,
                                   color = "black"),
        axis.text.y = element_text(size = 11,
                                   color = "black"),
        strip.text.x = element_text(size = 11,
                                    color = "black")) +
  scale_color_brewer(palette = "Dark2")

@@

```{r length-freq-p, fig.cap = "Length frequency histogram of Northern Pikeminnow caught using hook-and-line angling during the study."}
length_freq_p = gastric_df %>%
  ggplot(aes(length)) +
  geom_histogram(breaks = seq(150, 650, by = 50),
                 col = "black",
                 fill = "gray30",
                 alpha = .2) +
  labs(x = "Total Length (mm)",
       y = "Frequency") +
  xlim(c(100, 700)) +
  ylim(c(0, 800)) +
  scale_x_continuous(breaks = seq(0, 650, by = 50)) +
  scale_y_continuous(breaks = seq(0, 550, by = 50)) +
  theme(axis.text.x = element_text(size = 11,
                                   color = "black"),
        axis.text.y = element_text(size = 11,
                                   color = "black",
                                   vjust = 3)) +
  theme_classic()

@@

```{r bio-p, fig.cap = "The cumulative amount of fish (g) consumed by an individual Northern Pikeminnow during the peak DSR (fall) and NRR (spring) Chinook Salmon emigrations (top panel) and corresponding daily mean water temperatures (bottom panel). The black line is the median among diet scenarios (i.e., where 50% of the Northern Pikeminnow diet consists of fish) and the gray area shows the range among model scenarios (i.e., 10 - 90% of Northern Pikeminnow diet consists of fish). Daily mean water temperatures were summarized from six years of data available from the Shoup gage station. "}
spring_results$season = "Spring"
fall_results$season = "Fall"
bio_results = rbind(spring_results, fall_results)
bio_results$ymd = (ymd(bio_results$date))

pFish = bio_results %>%
  ggplot(aes(ymd, f50_g)) +
  geom_line(size = 1.15) +
  geom_ribbon(data = bio_results,
              aes(ymd,
                  ymin = f10_g,
                  ymax = f90_g),
              color = "grey65",
              alpha = 0.4) +
  theme_bw() +
  labs(y = "Fish consumed (g)",
       x = "",
       title = "") +
  facet_rep_wrap(~season,
                 scales = "free_x",
                 repeat.tick.labels = F) +
  theme(strip.background = element_rect(color = "white",
                                        fill = "white"),
        strip.text.x = element_text(size = 12),
        axis.text.x = element_blank(),
        axis.text.y = element_text(size = 11,
                                   color = "black"),
        axis.title.y = element_text(vjust = 1,
                                    size = 12),
        panel.grid.major.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.margin = unit(c(-.1, .3, -.3, .2), "cm"))

pTemp = bio_results %>%
  ggplot(aes(ymd, temperature_c)) +
  geom_line(color = "navyblue",
            size = 1.15) +
  theme_bw() +
  labs(y = expression("Water temp"*~degree*C),
       x = "Month",
       title = "") +
  facet_rep_wrap(~season,
                 scales = "free_x",
                 repeat.tick.labels = F) +
  theme(strip.background = element_rect(color = "white",
                                        fill = "white"),
        strip.text.x = element_blank(),
        axis.text.x = element_text(size = 11,
                                   color = "black"),
        axis.title.x = element_blank(),
        axis.text.y = element_text(size = 11,
                                   color = "black"),
        axis.title.y = element_text(vjust = 0.1,
                                    size = 12),
        panel.grid.major.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.margin = unit(c(-.1, .3, .1, .1), "cm"))

@@

```{r adult-imp-p, fig.cap = "The estimated number of DSR (fall) and NRR (spring) emigrants consumed by Northern Pikeminnow in Deadwater Slough (top panel) across a range of diet scenarios where 10-90% of the diet consists of juvenile Chinook salmon. The bottom panel provides the adult equivalents assuming a Lower Granite Dam smolt-to-adult rate (SAR) from McCann et al. 2019."}
adult_impact %>%
  mutate(stage = "Juv. Emigrant") %>%
  select(stage,
         season,
         perc_diet,
         starts_with("smolt")) %>%
  rename_with(.fn = ~ str_remove(., "smolt_"),
              .cols = starts_with("smolt")) %>%
  bind_rows(adult_impact %>%
              mutate(stage = "Adult Equivalent") %>%
              select(stage,
                     season,
                     perc_diet,
                     starts_with("adult")) %>%
              rename_with(.fn = ~ str_remove(., "adult_"),
                          .cols = starts_with("adult"))) %>%
  ggplot(aes(x = perc_diet,
             y = N,
             color = as.factor(perc_diet))) +
  geom_errorbar(aes(ymin = Lci,
                    ymax = Uci),
                width = 0.1) +
  geom_point(size = 4) +
  facet_grid(fct_rev(stage) ~ season,
             scales = "free_y") +
  scale_color_viridis_d(name = "Percent\nFish in Diet") +
  theme(axis.text.x = element_blank(),
        legend.position = "bottom",
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.text.y = element_text(size = 11,
                                   color = "black"),
        strip.text.x = element_text(size = 11,
                                    color = "black"),
        strip.text.y = element_text(size = 11,
                                    color = "black")) +
  labs(y = "Number Chinook Consumed")
